Step1_LoadData

### 2024-07-15 ProxySelection.Rmd
results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

_Step 0: Analytic data, Step 1: Proxy sources, Step 2: Emperical, Step 3: Recurrence_
```{r loading-data, warning=FALSE}
# ------------------- Select proxy based on the results from out2
# ------------------- change the code after Step 3: Recurrence
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)

load("data/analytic3cycles.RData")

@@

require(autoCovariateSelection)
step1 <- get_candidate_covariates(df = dfx,  
                                  domainVarname = "domain",
                                  eventCodeVarname = "icd10", 
                                  patientIdVarname = "idx",
                                  patientIdVector = patientIds,
                                  n = 200, 
                                  min_num_patients = 20)
out1 <- step1$covars_data
# ------------------- top 200 prevalent icd10 with min 20 patients

@@

**Method 1: Bross Formula**
```{r, warning=FALSE}
out3 <- get_prioritised_covariates(df = out2,
                                   patientIdVarname = "idx", 
                                   exposureVector = basetable$exposure,
                                   outcomeVector = basetable$outcome,
                                   patientIdVector = patientIds, 
                                   k = 100)
hdps.dim <- out3$autoselected_covariate_df

@@

require(WeightIt)
W.out <- weightit(ps.formula, 
                  data = hdps.data, 
                  estimand = "ATE",
                  method = "ps")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit <- glm(out.formula,
           data = hdps.data,
           weights = W.out$weights,
           family= binomial(link = "logit"))
fit.summary <- summary(fit)$coef["exposure",
                                 c("Estimate", 
                                   "Std. Error", 
                                   "Pr(>|z|)")]
fit.ci <- confint(fit, level = 0.95)["exposure", ]
fit.summary_with_ci <- c(fit.summary, fit.ci)
fit.summary_with_ci

@@

**Method 2: Hybrid Bross Formula & Lasso**
```{r, warning=FALSE}
set.seed(42)
proxy.list <- names(out3$autoselected_covariate_df[,-1])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit<-glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 1, 
                             nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.hybrid <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.hybrid)
fs.hybrid <- proxy.list.sel.hybrid

@@

_Before implementing other methods, drop the information from method 1 (Bross formula). Continue with the results from Step 3: Recurrence (table `out2`)._
```{r, warning=FALSE}
hdps.dim <- out2

@@

**Method 3: Pure Lasso**
```{r, warning=FALSE}
set.seed(42) # different seed -> different length for the selected proxy list
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                               x = covar.mat, 
                               type.measure='mse',
                               family="binomial",
                               alpha = 1, 
                               nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.ml <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.ml)
fs.lasso <- proxy.list.sel.ml
proxy.lasso <- paste0(fs.lasso, collapse = "+")
form.lasso <- paste0(c(covform, proxy.lasso), collapse = "+")
formula.lasso <- as.formula(paste0("exposure", "~", form.lasso))

require(WeightIt)
W.out.lasso <- weightit(formula.lasso, 
                        data = hdps.data, 
                        estimand = "ATE",
                        method = "ps")

@@

**Method 4: Elastic Net**
```{r, warning=FALSE}
set.seed(42)
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
elas.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 0.5, 
                             nfolds = 5)
coef.fit<-coef(elas.fit, s='lambda.min', exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.elastic <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.elastic)
fs.elastic <- proxy.list.sel.elastic

@@

require(WeightIt)
W.out.elastic <- weightit(formula.elastic, 
                       data = hdps.data, 
                       estimand = "ATE",
                       method = "ps")

@@

**Method 5: XGBoost**
```{r, warning=FALSE}
xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
                    max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
                    objective = "binary:logistic")

@@

require(WeightIt)
W.out.xgboost <- weightit(formula.xgboost, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

_GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
```{r, warning=FALSE}
gaOpt <- function(vars, IV.train, DV.train) {
	varNames <- colnames(IV.train) #getting names of all variables
	selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
	gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars

@@

require(WeightIt)
W.out.GA <- weightit(formula.GA, 
                         data = hdps.data, 
                         estimand = "ATE",
                         method = "ps")

@@

_(Long Running Time)_
```{r, results='hide'}
svmTrainOutcome <- hdps.data$outcome
svmTrainOutcome[svmTrainOutcome == 0] <- -1
svmTrainPreds <- data.frame(covar.mat)

@@

```{r, warning=FALSE}
fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
fs.svm <- proxy.list[proxy.list %in% fs.svm]
proxy.svm <- paste0(fs.svm, collapse = "+")
form.svm <- paste0(c(covform, proxy.svm), collapse = "+")
formula.svm <- as.formula(paste0("exposure", "~", form.svm))

require(WeightIt)
W.out.svm <- weightit(formula.svm, 
                        data = hdps.data, 
                        estimand = "ATE",
                        method = "ps")

@@

_(Long Running Time)_
```{r, warning=FALSE}
set.seed(42)
boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)
sel.variables.bor <- names(boruta_output$finalDecision)[which(boruta_output$finalDecision != "Rejected")]
fs.boruta <- proxy.list[proxy.list %in% sel.variables.bor]
proxy.boruta <- paste0(fs.boruta, collapse = "+")
form.boruta <- paste0(c(covform, proxy.boruta), collapse = "+")
formula.boruta <- as.formula(paste0("exposure", "~", form.boruta))

require(WeightIt)
W.out.boruta <- weightit(formula.boruta, 
                         data = hdps.data, 
                         estimand = "ATE",
                         method = "ps")

@@

**Method 9.1: Stepwise Regression (Forward)**
```{r}
set.seed(42)

@@

require(WeightIt)
W.out.forward <- weightit(formula.forward, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

**Method 9.2: Stepwise Regression (Backward)**
```{r}
stepwise_backward <- stepAIC(full_model, direction = "backward")
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

require(WeightIt)
W.out.backward <- weightit(formula.backward, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

**Method 9.3: Stepwise Regression (Both)**
```{r}
stepwise_both <- stepAIC(initial_model, 
                            scope = list(lower = initial_model, 
                                         upper = full_model), 
                            direction = "both")
fs.both <- all.vars(formula(stepwise_both))[-1]
fs.both <- proxy.list[proxy.list %in% fs.both]
proxy.both <- paste0(fs.both, collapse = "+")
form.both <- paste0(c(covform, proxy.both), collapse = "+")
formula.both <- as.formula(paste0("exposure", "~", form.both))

require(WeightIt)
W.out.both <- weightit(formula.both, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

Comparing the Results:
```{r}
sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 
                    sum_ci.xgboost, sum_ci.GA, sum_ci.svm, sum_ci.boruta,
                    sum_ci.forward, sum_ci.backward, sum_ci.both)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
```

@@

_Step 0: Analytic data, Step 1: Proxy sources, Step 2: Emperical, Step 3: Recurrence_
```{r loading-data, warning=FALSE, cache=TRUE}
# ------------------- Select proxy based on the results from out2
# ------------------- change the code after Step 3: Recurrence
load("data/analytic3cycles.RData")

@@

step1 <- get_candidate_covariates(df = dfx,  
                                  domainVarname = "domain",
                                  eventCodeVarname = "icd10", 
                                  patientIdVarname = "idx",
                                  patientIdVector = patientIds,
                                  n = 200, 
                                  min_num_patients = 20)
out1 <- step1$covars_data
# ------------------- top 200 prevalent icd10 with min 20 patients

@@

**Method 1: Bross Formula**
```{r, warning=FALSE, cache=TRUE}
out3 <- get_prioritised_covariates(df = out2,
                                   patientIdVarname = "idx", 
                                   exposureVector = basetable$exposure,
                                   outcomeVector = basetable$outcome,
                                   patientIdVector = patientIds, 
                                   k = 100)
hdps.dim <- out3$autoselected_covariate_df

@@

W.out <- weightit(ps.formula, 
                  data = hdps.data, 
                  estimand = "ATE",
                  method = "ps")
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit <- glm(out.formula,
           data = hdps.data,
           weights = W.out$weights,
           family= binomial(link = "logit"))
fit.summary <- summary(fit)$coef["exposure",
                                 c("Estimate", 
                                   "Std. Error", 
                                   "Pr(>|z|)")]
fit.ci <- confint(fit, level = 0.95)["exposure", ]
fit.summary_with_ci <- c(fit.summary, fit.ci)
fit.summary_with_ci

@@

**Method 2: Hybrid Bross Formula & Lasso**
```{r, warning=FALSE, cache=TRUE}
set.seed(42)
proxy.list <- names(out3$autoselected_covariate_df[,-1])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit<-glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 1, 
                             nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.hybrid <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.hybrid)
fs.hybrid <- proxy.list.sel.hybrid

@@

_Before implementing other methods, drop the information from method 1 (Bross formula). Continue with the results from Step 3: Recurrence (table `out2`)._
```{r, warning=FALSE, cache=TRUE}
hdps.dim <- out2

@@

**Method 3: Pure Lasso**
```{r, warning=FALSE, cache=TRUE}
set.seed(42) # different seed -> different length for the selected proxy list
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                               x = covar.mat, 
                               type.measure='mse',
                               family="binomial",
                               alpha = 1, 
                               nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.ml <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.ml)
fs.lasso <- proxy.list.sel.ml
proxy.lasso <- paste0(fs.lasso, collapse = "+")
form.lasso <- paste0(c(covform, proxy.lasso), collapse = "+")
formula.lasso <- as.formula(paste0("exposure", "~", form.lasso))

W.out.lasso <- weightit(formula.lasso, 
                        data = hdps.data, 
                        estimand = "ATE",
                        method = "ps")

@@

**Method 4: Elastic Net**
```{r, warning=FALSE, cache=TRUE}
set.seed(42)
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
elas.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 0.5, 
                             nfolds = 5)
coef.fit<-coef(elas.fit, s='lambda.min', exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.elastic <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.elastic)
fs.elastic <- proxy.list.sel.elastic

@@

W.out.elastic <- weightit(formula.elastic, 
                       data = hdps.data, 
                       estimand = "ATE",
                       method = "ps")

@@

**Method 5: XGBoost**
```{r, warning=FALSE, cache=TRUE}
xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
                    max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
                    objective = "binary:logistic")

@@

W.out.xgboost <- weightit(formula.xgboost, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

_GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
```{r, warning=FALSE, cache=TRUE}
gaOpt <- function(vars, IV.train, DV.train) {
	varNames <- colnames(IV.train) #getting names of all variables
	selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
	gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars

@@

W.out.GA <- weightit(formula.GA, 
                         data = hdps.data, 
                         estimand = "ATE",
                         method = "ps")

@@

_(Long Running Time)_
```{r, warning=FALSE, cache=TRUE}
svmTrainOutcome <- hdps.data$outcome
svmTrainOutcome[svmTrainOutcome == 0] <- -1
svmTrainPreds <- data.frame(covar.mat)

@@

```{r, warning=FALSE, cache=TRUE}
fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
fs.svm <- proxy.list[proxy.list %in% fs.svm]
proxy.svm <- paste0(fs.svm, collapse = "+")
form.svm <- paste0(c(covform, proxy.svm), collapse = "+")
formula.svm <- as.formula(paste0("exposure", "~", form.svm))

W.out.svm <- weightit(formula.svm, 
                        data = hdps.data, 
                        estimand = "ATE",
                        method = "ps")

@@

_(Long Running Time)_
```{r, warning=FALSE, cache=TRUE}
set.seed(42)
boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)
sel.variables.bor <- names(boruta_output$finalDecision)[which(boruta_output$finalDecision != "Rejected")]
fs.boruta <- proxy.list[proxy.list %in% sel.variables.bor]
proxy.boruta <- paste0(fs.boruta, collapse = "+")
form.boruta <- paste0(c(covform, proxy.boruta), collapse = "+")
formula.boruta <- as.formula(paste0("exposure", "~", form.boruta))

W.out.boruta <- weightit(formula.boruta, 
                         data = hdps.data, 
                         estimand = "ATE",
                         method = "ps")

@@

**Method 9.1: Stepwise Regression (Forward)**
```{r, warning=FALSE, cache=TRUE}
set.seed(42)

@@

W.out.forward <- weightit(formula.forward, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

**Method 9.2: Stepwise Regression (Backward)**
```{r, warning=FALSE, cache=TRUE}
stepwise_backward <- stepAIC(full_model, direction = "backward")
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

W.out.backward <- weightit(formula.backward, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

**Method 9.3: Stepwise Regression (Both)**
```{r, warning=FALSE, cache=TRUE}
stepwise_both <- stepAIC(initial_model, 
                            scope = list(lower = initial_model, 
                                         upper = full_model), 
                            direction = "both")
fs.both <- all.vars(formula(stepwise_both))[-1]
fs.both <- proxy.list[proxy.list %in% fs.both]
proxy.both <- paste0(fs.both, collapse = "+")
form.both <- paste0(c(covform, proxy.both), collapse = "+")
formula.both <- as.formula(paste0("exposure", "~", form.both))

W.out.both <- weightit(formula.both, 
                          data = hdps.data, 
                          estimand = "ATE",
                          method = "ps")

@@

Comparing the Results:
```{r, warning=FALSE, cache=TRUE}
sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 
                    sum_ci.xgboost, sum_ci.GA, sum_ci.svm, sum_ci.boruta,
                    sum_ci.forward, sum_ci.backward, sum_ci.both)
